Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-07 main.tex
rewrote the "on average" with more concrete numbers

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, often with an invalid over-optimistic schedule that exceeds
the bound on memory.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline,
the makespans of \heftblc are $8.0\%$
worse, and those found by \heftmm are $82.6\%$ worse. These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft correspond to invalid schedules.

 %   \skug{TODO: how much worse are makespans for SUCCESSFUL hefts? presulmably almost identical}

>>>>

We also report in  Figure~\ref{fig:ms-relations-by-workflow} the relative makespan found
by the memory-aware heuristics, normalized to the
makespan achieved by \heft, often with an invalid over-optimistic schedule that exceeds
the bound on memory.
%    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
%    makespans found by the baseline (including invalid ones), by workflow size.
\new{The makespans found by \heftbl are $<13\%$ worse than those found by the baseline for workflows with less than \numprint{2000}
tasks, and up to $27\%$ worse for the largest workflows.
The makespans of \heftblc are very similar,being $<17\%$ worse on smallest workflows, $19$-$28\%$ worse on middle-sized,
and up to $30\%$ worse on the largest workflows.
The makespans found by \heftmm are $25$-$30\%$ worse on the smallest workflows, $40$-$70\%$ on middle-sized and up to
$210\%$ on the largest ones. These are still very encouraging results,
in particular for \heftbl and \heftblc, since the makespans of \heft correspond to invalid schedules.
}
 %   \skug{TODO: how much worse are makespans for SUCCESSFUL hefts? presulmably almost identical}
